GSEA datasets for FDR benchmarking

### 2018-02-23 datasets/GSEA/gsea.Rmd
Added source and description of mouse data

pr <- designBen %>% buildBench( res, ftCols="ind_covariate")
assayNames(pr) <- "qvalue"
pr <- addDefaultMetrics(pr, metrics="rejections")

@@

# Same analysis but using the HSC-MPP dataset from Nina

Add some description of the HSC-MPP dataset.

@@

>>>>

pr <- designBen %>% buildBench( res, ftCols="ind_covariate")
assayNames(pr) <- "qvalue"
pr <- addDefaultMetrics(pr)

@@

# GSEA of genes differentially expressed upon blood cell differentiation in mouse

As a second dataset, we will use the mouse data from the paper by [Cabezas-Wallscheid et al. (Cell stem Cell, 2014)](https://www.sciencedirect.com/science/article/pii/S1934590914003014?via%3Dihub). The dataset consists of RNA-seq data from mouse hematopoietic stem cells and 4 multipotent progenitor lineages.

@@

For this analysis, we will test each gene for differences in expression between hematopoietic stem cells and multipotent progenitors (fraction 1).
